Supporting information: Copulas and their potential for ecology

### 2019-10-03 Paper.Rmd
edits to Q2 sections, through first model methods and results

Having demonstrated that non-normal copula structure and asymmetric tail associations are 
common in ecological variables, we 
addressed Q2 by exploring, using models, three possible mechanisms
by which these phenomena may arise. 
<!--***DAN: Maybe insert some text indicating these are first, exploratory models, and are not intended to comprehensively explore
a mechanism (that can be done in future work), but rather to get a sense
for whether observed copula structure may be partly due to the
mechanism, and whether the mechanism is worthy of more comprehensive
exploration in that connection in future work. One way these are noncomprehensive
explorations is that I chose particular limited sets of parameters.-->
The first mechanism relates to the ideas in the Introduction about 
Liebig's law of the minimum, and to nonlinear influences of environmental
variables on ecological variables.
If an environmental variables influences an ecological variable 
more strongly in one of its tails, we explored whether the ecological
variable could then exhibit asymmetric tail dependence across space.
Let $E_i(t)$ be an ecological variable 
measured at location $i$ ($i=1,2$) at time $t$.
Assume the dynamics 
$E_i(t+1)=bE_i(t)+g(\epsilon_i(t))+a \delta_i(t)$, where 
the $\delta_i(t)$ are standard-normally distributed 
and independent across time and locations, $a=0.2$,
$b=0.1, -0.1, 0.5, -0.5$ in different simulations, and 
the $(\epsilon_1(t),\epsilon_2(t))$ were drawn, independently through
time, from a bivariate normal distribution with $\var(\epsilon_i)=1$ and 
$\cov(\epsilon_1,\epsilon_2)=0.8$.
The function $g$ describes how the environment $\epsilon_i(t)$ influences
$E_i(t)$. We used $g$ equal to $g_1$ or $g_2$ in different simulations:
$g_1(\epsilon)$ equals $\epsilon$ if $\epsilon<0$ and $0$ otherwise;
$g_2(\epsilon)$ equals $\epsilon$ if $\epsilon>0$ and $0$ otherwise. Thus
$g_1$ represents environmental effects that negatively impact populations,
and that occur only below a threshold of $\epsilon=0$; 
and $g_2$ represents effects that positively impact populations and 
that occur only above a threshold of $\epsilon=0$.
Negative values of $b$ correspond to overcompensating dynamics 
and positive values to undercompensating dynamics; larger $|b|$
means slower return to equilibrium after a disturbance.

For each $b$ and $g_i$, we simulated the model for $25000$ time
steps and retained the $E_i(t)$ for the final $2500$ time 
steps. We applied our model selection algorithms and 
nonparametric statistics (see section on methods for Q1) to these 
outputs to discover if the model could
produce non-normal copula structure and asymmetric tail dependence in the 
$E_i(t)$. Because $(\epsilon_1,\epsilon_2)$
and $(\delta_1,\delta_2)$ have normal copula structure (they were drawn
from bivariate normal distributions), the Moran 
mechanism analyzed below 
does not operate here.
<!--***DAN: You may also want to have some additional commentary in the Discussion on
how the models and related models can be explored more comprehensively. In fact you may already have some of that, though you may want to beef it up. You may
want to insert a point at the end of the Methids section here again emphasizing
that these are simple models for an initial exploration, and we discuss in the 
Discussion how...-->

@@

Our model with asymmetric environmental effects 
produces outputs with visually apparent asymmetry 
of tail dependence, to an extent that depended on the value of $b$;
thus this is a mechanism that can produce non-normal copula structure and
asymmetric tail dependence across space in ecological variables.
<!--***DAN: move the following to the end of this part-->
This result is represented in Fig. \ref{MasterFigure} as the solid box around 
"Nonlinear environmental effects, Liebig's law" and the arrows labelled "A".
It is explained in the Discussion why the box and some of those arrows 
are solid, instead of dashed, although the results we 
present in this section are theoretical.
<!--***DAN: move the above to the end of this part-->
For $b=0.1$ (Fig. \ref{fig_ms_asym_b_0.1}) and $b=-0.1$ 
(Fig. \ref{SM-fig_ms_asym_b_-0.1_0.5_-0.5}A,B), 
for both $g_1$ and $g_2$,
asymmetry of tail dependence was strong; for 
$b=\pm 0.5$, asymmetry was weaker but still apparent
(Fig. \ref{SM-fig_ms_asym_b_-0.1_0.5_-0.5}C-F).
<!--***DAN: Shyamolina, can you please combine Figs S24-S26 into one single figure
with 6 panels? Please also search for citations in the main text and sup mat that 
used to refer to the three figures and replace them with a citation to the
new, combined figure.
***Shya: Done.-->
Lower-tail (respectively, upper-tail) spatial dependence in 
effects of noise ($g_1$, respectively, $g_2$) 
produced lower-tail (respectively, upper-tail) spatial 
dependence in the ecological variable.
Model selection results (Table \ref{SM-tab_summary_stat_asym_sens}) confirmed that
ecological outputs had non-normal copula structure, but did not always reflect 
asymmetry of tail dependence, perhaps because those methods measured
dependence in the extreme tails. Results using our nonparametric statistics, however,
reflected the visually apparent asymmetry (Tables \ref{SM-tab_stat_npa_asym}). 
<!--***DAN: Simplify as follows, maybe:
1) get rid of table S10 (you will have to change the methods so it no longer says we
do our model selection analysis here)
2) simplify table S11 so it only shows the cor results (also means a change to methods)
and then maybe bring the resulting table to main text?
-->

<!--***DAN: Shyamolina, can you please simplify Table S11 so it only shows the cor
results? That also means the third column will be unnecessary. Please do this as follows:
1) keep but comment out the code that produces the old table; 2) write new code (presumably
starting from a copy of the old code) that makes the new, simpler version of the table. 
That will make it very easy to produce the old version again if we ever want to.
***Shya: Done.-->

@@

The hypothesis that characteristics of 
spatial copula structure and tail dependence
in an ecological variable can be inherited from an environmental 
variable was largely confirmed; 
<!--***DAN: You are using language about confirming hypotheses, here and elsewhere,
but this may rub some people the wrong way because we have not confirmed anything
empirically, we are just doing models, and only a cursory exploration of each
model, at that! So change the language.-->
however, similarities between environmental- and 
ecological-variable copula structure were reduced when 
dynamics were strongly nonlinear.
Thus this is a mechanism that can produce non-normal copula structure and
asymmetric tail dependence 
<!--****DAN: Don't firget to replace @tail dependence@ by @tail asociation@ as appropriate-->
across space in ecological variables.
<!--***DAN: move the below to end of this part-->
This result is represented in Fig. \ref{MasterFigure} as the dashed box around 
"Moran effects" and the arrows labelled "B".
<!--***DAN: move the above to end of this part-->
For simulations using AR(1) models, copula 
statistics were always very similar for noise and populations 
(Fig \ref{fig_Cause4copula_scatter_C_kend_ar1}, 
\ref{SM-fig_Cause4copula_C_kend_ar1}-\ref{SM-fig_Cause4copula_SJ_kend_ar1}),
though there were significant but minor differences for some statistics
and simulations.
For weak noise and our nonlinear model, copula statistics
were again very similar for noise and model outputs 
(Figs \ref{SM-fig_Cause4copula_C_kend_sRicker_nsd_0.1}-\ref{SM-fig_Cause4copula_SJ_kend_sRicker_nsd_1}).
Though there were again significant but small differences for some statistics
and simulations, the hypothesis was supported that copula 
structure in the noise translates
to similar but not identical copula structure in output populations. 
Since many ecological models are nonlinear, this result provides the 
expectation that there will be a Moran-effect-like correspondence 
between noise and model-output copula structure across space 
for typical ecological dynamics,
as long as noise is small enough that dynamics stay relatively close
to the model equilibrium. Results that hold for "weak noise" in this sense
are common in ecology. 
We repeated the analysis with $r=1.3$, with similar results. The deterministic 
one-habitat-patch Ricker model exhibits a monotonic approach to a stable equilibrium
at $K$ when $r<1$ (undercompensating dynamics, e.g., the value $r=0.5$ used initially), 
but exhibits an oscillatory approach to $K$ when $r>1$ (overcompensating
dynamics, e.g., $r=1.3$).

>>>>

Having demonstrated that non-normal copula structure and asymmetric tail associations are 
common in ecological variables, we 
addressed Q2 by exploring, using models, three possible mechanisms
by which these phenomena may arise. 
Models presented are initial explorations, only, of whether the proposed mechanisms have the 
potential to explain observed patterns. As such, simple models were used, 
and comprehensive explorations of
model parameter space and alternative model formulations were left for future work.

The first mechanism relates to the ideas in the Introduction about 
Liebig's law of the minimum, and to nonlinear influences of environmental
variables on ecological variables.
If an environmental variables influences an ecological variable 
disproportionately strongly in one of its tails, we explored whether the ecological
variable could then exhibit asymmetric tail dependence across space.
Let $E_i(t)$ be an ecological variable 
measured at location $i$ ($i=1,2$) at time $t$.
Assume the dynamics 
$E_i(t+1)=bE_i(t)+g(\epsilon_i(t))+a \delta_i(t)$, where 
the $\delta_i(t)$ are standard-normally distributed 
and independent across time and locations, $a=0.2$,
$b=0.1, -0.1, 0.5, -0.5$ in different simulations, and 
the $(\epsilon_1(t),\epsilon_2(t))$ were drawn, independently through
time, from a bivariate normal distribution with $\var(\epsilon_i)=1$ and 
$\cov(\epsilon_1,\epsilon_2)=0.8$. Thus basic ecological dynamics follow the
very simple AR(1) formulation, influenced by a "regional" environmental factor which
is correlated across locatons ($\epsilon$) and by a local factor ($\delta$). 
The function $g$ describes how the environmental factor $\epsilon_i(t)$ influences
$E_i(t)$. We used $g$ equal to $g_1$ or $g_2$ in different simulations:
$g_1(\epsilon)$ equals $\epsilon$ if $\epsilon<0$ and $0$ otherwise;
$g_2(\epsilon)$ equals $\epsilon$ if $\epsilon>0$ and $0$ otherwise. Thus
$g_1$ represents environmental effects that negatively impact populations,
and that occur only below a threshold of $\epsilon=0$; 
and $g_2$ represents effects that positively impact populations and 
that occur only above a threshold of $\epsilon=0$.
The values of $b$ selected provide a modicum of exploration of the potential
for ecological dynamics to influence how complex dependencies between
the $E_i(t)$ may arise: 
negative values of $b$ correspond to overcompensating dynamics 
and positive values to undercompensating dynamics; larger $|b|$
means slower return to equilibrium after a disturbance.

For each $b$ and $g_i$, we simulated the model for $25000$ time
steps and retained the $E_i(t)$ for the final $2500$ time 
steps. We applied our 
nonparametric statistic $\cor_{0,0.1}-\cor_{0.9,1}$ 
and our Spearman- or Kendall-preserving normal-copula 
surrogates (see section on methods for Q1) to these 
outputs to discover if the model could
produce asymmetric tail associations (and therefore non-normal copula structure)
between the $E_i(t)$. Because $(\epsilon_1,\epsilon_2)$
and $(\delta_1,\delta_2)$ have normal copula structure (they were drawn
from bivariate normal distributions), the Moran 
mechanism analyzed below does not operate here.
<!--***DAN: You may also want to have some additional commentary in the Discussion on
how the models and related models can be explored more comprehensively. In fact you may already have some of that, though you may want to beef it up. You may
want to insert a point at the end of the Methids section here again emphasizing
that these are simple models for an initial exploration, and we discuss in the 
Discussion how...-->

<!--***DAN: stopped here in Q2 methods in order to go on to the correspondng
section of Q2 results-->

@@

Our model with asymmetric environmental effects 
produced outputs with visually apparent asymmetry 
of tail associations between the ecological variables $E_i$ in the two locations, 
to an extent that depended on the value of $b$.
For $b=0.1$ (Fig. \ref{fig_ms_asym_b_0.1}) and $b=-0.1$ 
(Fig. \ref{SM-fig_ms_asym_b_-0.1_0.5_-0.5}A,B), 
for both $g_1$ and $g_2$,
asymmetry of tail association was strong; for 
$b=\pm 0.5$, asymmetry was weaker but still apparent
(Fig. \ref{SM-fig_ms_asym_b_-0.1_0.5_-0.5}C-F).
Lower-tail (respectively, upper-tail) spatial associations in the 
effects of noise ($g_1$, respectively, $g_2$) 
produced lower-tail (respectively, upper-tail) spatial 
associations in the ecological variable, $E_i$.
Results using our statistic $\cor_{0,0.1}-\cor_{0.9,1}$ 
strongly reflected the visually apparent asymmetry (Tables \ref{tab_stat_npa_asym}). 
Thus asymmetry of environmental effects is a mechanism that may be partly 
responsible for non-normal copula structure and
asymmetric tail dependence across space in ecological variables.
This result is represented in Fig. \ref{MasterFigure} as the solid box around 
"Nonlinear environmental effects, Liebig's law" and the arrows labelled "A".
It is explained in the Discussion why the box and some of those arrows 
are solid, instead of dashed, although the results we 
present so far in this section are theoretical.

@@

```{r tab_stat_npa_asym_simple,echo=F,results="markup"}
library(kableExtra)

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.5.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}

ind_corstat<-which(tab_stat_npa_asym$Statistic %in% c("cor$_{FS}$-cor$_{LS}$"))
tab_corstat_asym<-tab_stat_npa_asym[ind_corstat,]
tab_corstat_asym<-tab_corstat_asym[,-1]

#gtext<-c("b=0.1, g$_{1}$","b=0.1, g$_{2}$","b=-0.1, g$_{1}$","b=-0.1, g$_{2}$","b=0.5, g$_{1}$","b=0.5, g$_{2}$","b=-0.5, #g$_{1}$","b=-0.5, g$_{2}$")
#tab_stat_npa_asym<-cbind(gtext,tab_corstat_asym)

tab_corstat_asym<-cbind(b=c(0.1,0.1,-0.1,-0.1,0.5,0.5,-0.5,-0.5),
  g=c("g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$"),tab_corstat_asym)

rownames(tab_corstat_asym)<-NULL

knitr::kable(tab_corstat_asym, booktabs = T, 
             format = "latex",linesep = "",escape=F, 
             caption.short = "Asymmetric sensitivity model, nonparametric statistics results",
             caption ="Asymmetric sensitivity model, nonparametric statistics results. 
Outputs of simulations from the first model detailed in 
the methods section for Q2 (i.e., Figs \\ref{fig_ms_asym_b_0.1} and 
\\ref{SM-fig_ms_asym_b_-0.1_0.5_-0.5}) were subjected to nonparamtric statistical 
analyses decribed in the methods section for Q1. The statistic cor$_{FS}$ - cor$_{LS}$ was computed for the
output of the model with the indicated b and g, and the value was compared to 1000 values
of the same statistic computed on surrogate time series randomized to have normal copula structure
(see methods for Q1). A table entry $<X$ (respectively, $>X$) indicates the value of the 
given statistic on the data was less (respectively, more) than its value on $X$ of the 
surrogates, so entries of the form $<X$ (respectively, $>X$) for $X$ equal to $975$ or above 
indicate that upper-tail (respectively, lower-tail) dependence was significantly stronger than 
lower-tail dependence compared to a normal-copula null hypothesis. `FS' stands for `first slice'
and refers to the bounds 0 to 0.1; `LS' stands for `last slice' and refers to the bounds
0.9 to 1.\\label{tab_stat_npa_asym}")
```

<!--***DAN: got to here so far in editing the result for Q2-->

<!--Second mechanism, the Moran one-->
The hypothesis that characteristics of 
spatial copula structure and tail dependence
in an ecological variable can be inherited from an environmental 
variable was largely confirmed; 
<!--***DAN: You are using language about confirming hypotheses, here and elsewhere,
but this may rub some people the wrong way because we have not confirmed anything
empirically, we are just doing models, and only a cursory exploration of each
model, at that! So change the language.-->
however, similarities between environmental- and 
ecological-variable copula structure were reduced when 
dynamics were strongly nonlinear.
Thus this is a mechanism that can produce non-normal copula structure and
asymmetric tail dependence 
<!--****DAN: Don't firget to replace @tail dependence@ by @tail asociation@ as appropriate-->
across space in ecological variables.
<!--***DAN: move the below to end of this part-->
This result is represented in Fig. \ref{MasterFigure} as the dashed box around 
"Moran effects" and the arrows labelled "B".
<!--***DAN: move the above to end of this part-->
For simulations using AR(1) models, copula 
statistics were always very similar for noise and populations 
(Fig \ref{fig_Cause4copula_scatter_C_kend_ar1}, 
\ref{SM-fig_Cause4copula_C_kend_ar1}-\ref{SM-fig_Cause4copula_SJ_kend_ar1}),
though there were significant but minor differences for some statistics
and simulations.
For weak noise and our nonlinear model, copula statistics
were again very similar for noise and model outputs 
(Figs \ref{SM-fig_Cause4copula_C_kend_sRicker_nsd_0.1}-\ref{SM-fig_Cause4copula_SJ_kend_sRicker_nsd_1}).
Though there were again significant but small differences for some statistics
and simulations, the hypothesis was supported that copula 
structure in the noise translates
to similar but not identical copula structure in output populations. 
Since many ecological models are nonlinear, this result provides the 
expectation that there will be a Moran-effect-like correspondence 
between noise and model-output copula structure across space 
for typical ecological dynamics,
as long as noise is small enough that dynamics stay relatively close
to the model equilibrium. Results that hold for "weak noise" in this sense
are common in ecology. 
We repeated the analysis with $r=1.3$, with similar results. The deterministic 
one-habitat-patch Ricker model exhibits a monotonic approach to a stable equilibrium
at $K$ when $r<1$ (undercompensating dynamics, e.g., the value $r=0.5$ used initially), 
but exhibits an oscillatory approach to $K$ when $r>1$ (overcompensating
dynamics, e.g., $r=1.3$).

### 2019-10-03 SupportingInformation.Rmd
edits to Q2 sections, through first model methods and results

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.1$ (A-B), $b=0.5$ (C-D) and $b=-0.5$ (E-F).\label{fig_ms_asym_b_-0.1_0.5_-0.5}}
\end{center}
\end{figure}

<!--Displaying summary table with model selection results from asymmetric dependence analysis-->
```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[c(1:6),]
rownames(summary_stat)<-c("Best-fit copula AICw","Normal copula AICw","Model-avg. LT","Model-avg. UT","p, CvM","p, KS")
knitr::kable(summary_stat, booktabs = T, escape=F,
             format = "latex", linesep = "",
             digits=4, col.names=c("b=0.1, g$_{1}$","b=0.1, g$_{2}$",
                                   "b=-0.1, g$_{1}$","b=-0.1, g$_{2}$",
                                   "b=0.5, g$_{1}$","b=0.5, g$_{2}$",
                                   "b=-0.5, g$_{1}$","b=-0.5, g$_{2}$"),
      caption.short="Asymmetric sensitivity model, model selection results",
      caption="Asymmetric sensitivity model, model selection results. 
The output of simulations from the first model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1_0.5_-0.5}) were subjected to the model 
selection procedures detailed in the 
methods section for Q1. Best-fit copula AICw: the AIC weight of the best-fitting copula family;
Normal copula AICw: the AIC weight of the normal copula family; Model-avg. LT: the lower-tail 
statistic, weighted-averaged across models using AICw; Model-avg. UT: same, but for the 
upper-tail statistic; p, CvM: p-value for goodness of fit test of the best-fitting copula
family using the test based on the Cramer-von Mises statistic; p, KS: p-value for goodness of fit 
test of the best-fitting copula family using the test based on the Kolmogorov-Smirnov 
statistic.\\label{tab_summary_stat_asym_sens}")
```

<!--*** Keeping old complex table for future use:
Displaying summary table with non-parametric approach results of asymmetric dependence analysis
```{r tab_stat_npa_asym,echo=F,results="markup"}
library(kableExtra)

@@

<!---Simpler version: Displaying summary table with non-parametric approach results of asymmetric dependence analysis--->
```{r tab_stat_npa_asym_simple,echo=F,results="markup"}
library(kableExtra)

@@

knitr::kable(tab_corstat_asym, booktabs = T, 
             format = "latex",linesep = "",escape=F, 
             caption.short = "Asymmetric sensitivity model, nonparametric statistics results",
             caption ="Asymmetric sensitivity model, nonparametric statistics results. 
The output of simulations from the first model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1_0.5_-0.5}) were subjected to nonparamtric statistical 
analyses decribed in the methods section for Q1. The statistic ($cor_{FS} - cor_{LS}$) was computed for the
output of the model with the indicated b and g, and the value was compared to 1000 values
of the same statistic computed on surrogate time series randomized to have normal copula structure
(see methods for Q1). A table entry $<X$ (respectively, $>X$) indicates the value of the 
given statistic on the data was less (respectively, more) than its value on $X$ of the 
surrogates, so entries of the form $<X$ (respectively, $>X$) for $X$ equal to $975$ or above 
indicate that upper-tail (respectively, lower-tail) dependence was significantly stronger than 
lower-tail dependence compared to a normal-copula null hypothesis. `FS' stands for `first slice'
and refers to the bounds 0 to 0.1; `LS' stands for `last slice' and refers to the bounds
0.9 to 1.\\label{tab_stat_npa_asym}")
```

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf}
\caption[Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using different model parameters]{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.1$ (A-B), $b=0.5$ (C-D) and $b=-0.5$ (E-F).\label{fig_ms_asym_b_-0.1_0.5_-0.5}}
\end{center}
\end{figure}

<!--Displaying summary table with model selection results from asymmetric dependence analysis-->
<!--Decided to remove this from the AER version
```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[c(1:6),]
rownames(summary_stat)<-c("Best-fit copula AICw","Normal copula AICw","Model-avg. LT","Model-avg. UT","p, CvM","p, KS")
knitr::kable(summary_stat, booktabs = T, escape=F,
             format = "latex", linesep = "",
             digits=4, col.names=c("b=0.1, g$_{1}$","b=0.1, g$_{2}$",
                                   "b=-0.1, g$_{1}$","b=-0.1, g$_{2}$",
                                   "b=0.5, g$_{1}$","b=0.5, g$_{2}$",
                                   "b=-0.5, g$_{1}$","b=-0.5, g$_{2}$"),
      caption.short="Asymmetric sensitivity model, model selection results",
      caption="Asymmetric sensitivity model, model selection results. 
The output of simulations from the first model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1_0.5_-0.5}) were subjected to the model 
selection procedures detailed in the 
methods section for Q1. Best-fit copula AICw: the AIC weight of the best-fitting copula family;
Normal copula AICw: the AIC weight of the normal copula family; Model-avg. LT: the lower-tail 
statistic, weighted-averaged across models using AICw; Model-avg. UT: same, but for the 
upper-tail statistic; p, CvM: p-value for goodness of fit test of the best-fitting copula
family using the test based on the Cramer-von Mises statistic; p, KS: p-value for goodness of fit 
test of the best-fitting copula family using the test based on the Kolmogorov-Smirnov 
statistic.\\label{tab_summary_stat_asym_sens}")
```
-->

<!--*** Keeping old complex table for future use, simpler version now displayed in main text:
Displaying summary table with non-parametric approach results of asymmetric dependence analysis
```{r tab_stat_npa_asym,echo=F,results="markup"}
library(kableExtra)

@@

<!---Simpler version: Displaying summary table with non-parametric approach results of asymmetric dependence analysis--->
<!--
```{r tab_stat_npa_asym_simple,echo=F,results="markup"}
library(kableExtra)

@@

knitr::kable(tab_corstat_asym, booktabs = T, 
             format = "latex",linesep = "",escape=F, 
             caption.short = "Asymmetric sensitivity model, nonparametric statistics results",
             caption ="Asymmetric sensitivity model, nonparametric statistics results. 
Outputs of simulations from the first model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1_0.5_-0.5}) were subjected to nonparamtric statistical 
analyses decribed in the methods section for Q1. The statistic cor$_{FS}$ - cor$_{LS}$ was computed for the
output of the model with the indicated b and g, and the value was compared to 1000 values
of the same statistic computed on surrogate time series randomized to have normal copula structure
(see methods for Q1). A table entry $<X$ (respectively, $>X$) indicates the value of the 
given statistic on the data was less (respectively, more) than its value on $X$ of the 
surrogates, so entries of the form $<X$ (respectively, $>X$) for $X$ equal to $975$ or above 
indicate that upper-tail (respectively, lower-tail) dependence was significantly stronger than 
lower-tail dependence compared to a normal-copula null hypothesis. `FS' stands for `first slice'
and refers to the bounds 0 to 0.1; `LS' stands for `last slice' and refers to the bounds
0.9 to 1.\\label{tab_stat_npa_asym}")
```
-->
